Author disambiguation of large-scale semi-labeled collections of scientific articles

### 2015-08-18 paper.tex
save

\begin{enumerate}
  \item There are different
  ways of transcripting an author name or some of signatures contain a typo
  (e.g., "Mueller, R." and "Muller, R.", "Tchaikovsky, P." and "Czajkowski, P.").

  \item An author has multiple surnames and, on some of his signatures, all the surnames but the
  last one are contained within given names (e.g., "Martinez Torres, A." and "Torres, A.
  Martinez").

  \item An author has multiple surnames and, on some of his signatures, only the first surname is
  present (e.g., "Smith-Jones, A." and "Smith, A.")

  \item An author as multiple given names and they are not always mentioned on his signatures (e.g.,
  "Smith, Jack" and "Smith, A. J.")

@@

In the case of multiple surnames (cases 2 and 3), we further propose to block
signatures in two phases. In the first phase, all the signatures with  one
surname are clustered together. Every different surname token creates a new
block. In the second phase, the signatures  with multiple surnames are compared
with the blocks for the first and last surname.  If the first surnames of an
author were already used as the last given names on some of the signatures, the
new signature is assigned to the block of the last surname (case 2). Otherwise,
the signature is assigned to the block of the first surname (case 3). Finally,
to prevent the creation of too large blocks, signatures are further divided
along their first given name initial.  Cases 4 and 5 are therefore not
explicitly handled.

>>>>

\begin{enumerate}
  \item There are different
  ways of transcripting an author name or signatures contain a typo
  (e.g., "Mueller, R." and "Muller, R.", "Tchaikovsky, P." and "Czajkowski, P.").

  \item An author has multiple surnames and, on some signatures, all the surnames but the
  last one are contained within given names (e.g., "Martinez Torres, A." and "Torres, A.
  Martinez").

  \item An author has multiple surnames and, on some signatures, only the first surname is
  present (e.g., "Smith-Jones, A." and "Smith, A.")

  \item An author as multiple given names and they are not always all mentioned (e.g.,
  "Smith, Jack" and "Smith, A. J.")

@@

In the case of multiple surnames (cases 2 and 3), we further propose to block
signatures in two phases. In the first phase, all the signatures with  one
surname are clustered together. Every different surname token creates a new
block. In the second phase, the signatures  with multiple surnames are compared
with the blocks for the first and last surname.  If the first surnames of an
author were already used as the last given names on some of the signatures, the
new signature is assigned to the block of the last surname (case 2). Otherwise,
the signature is assigned to the block of the first surname (case 3). Finally,
to prevent the creation of too large blocks, signatures are further divided
along their first given name initial.  Cases 4 and 5 are not
explicitly handled.
